### 2019-10-25 paper/conclusion.tex
Addressed issues

\section{Conclusion} \label{Conclusion}

Five different types of initial fissile loadings are considered to investigate 
transitioning to the thorium fuel cycle in the SD-TMSR. We adopted two 
different feed mechanisms: thorium feed mechanism and non-thorium feed 
mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
performed with reactor-grade Pu, TRU, and $^{233}$U as initial fissile 
materials. Additionally, the dynamics of the effective multiplication factor 
$k_{eff}$, major isotopes mass, neutron energy spectrum, and essential safety 
parameters have been investigated.

>>>>

\section{Conclusion} \label{Conclusion}
Five different types of initial fissile loadings have been studied for 
transitioning to the thorium fuel cycle in the Single-fluid Double-zone 
Thorium-based Molten Salt Reactor (SD-TMSR). We 
adopted two different feed mechanisms: thorium feed mechanism and non-thorium 
feed mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
performed with reactor-grade Pu, TRU, and $^{233}$U as initial fissile 
materials. Additionally, the dynamics of the effective multiplication factor 
$k_{eff}$, major isotopes mass, neutron energy spectrum, and essential safety 
parameters have been investigated.

### 2019-10-25 paper/results.tex

Table~\ref{tab:tcoe} summarizes temperature coefficients calculated for three 
different initial fissile loads at startup and at equilibrium. By propagating 
the $k_{eff}$ statistical error provided by SERPENT-2, uncertainty for each 
temperature coefficient is calculated using the following formula:
\begin{align}
\delta\alpha &= \abs{\frac{1}{T_{i+1} - T_i}} \sqrt{\frac{\delta 
		k_{eff}^2(T_{i+1})}{k_{eff}^4(T_{i+1})}  
	+ \frac{\delta k_{eff}^2(T_i)}{k_{eff}^4(T_i)}}
\intertext{where}
\delta k_{eff} &= \mbox{statistical error for $k_{eff}$ from SERPENT-2 
output.} 
\nonumber
\end{align}
Other sources of uncertainty are neglected, such as cross-section measurement 
error and approximations inherent in the density dependence on temperature.

When the fuel salt temperature increases, the density of the salt decreases; 
however, the total volume of fuel salt in the core remains constant because it
is bounded by the vessel. When the graphite temperature increases, the density 
of graphite decreases, creating additional space for the salt. The 
cross-section temperatures for the fuel and moderator were changed from 900 to 
1000 K to determine the temperature coefficients. This work considers five 
different cases:
\begin{enumerate}
	\item Fuel salt temperature (Doppler Effect) rising from 900 to 1000 K 	
	(first row in Table~\ref{tab:tcoe}).
	\item Fuel salt density decreasing from 3.3 to 3.233 g/cm$^3$ 
	(density change caused by temperature increase from	900 to 1000 K).
	\item Total fuel salt temperature (Doppler+density) rising from 900 to 
	1000 K.	
	\item Graphite temperature (Doppler Effect) rising from 900 to 1000 K.
	\item Whole reactor temperature rising from 900 K to 1000 K.
\end{enumerate}

In the first case, the fuel temperature change only impacts cross-section 
temperature. In the second case, changes in the fuel temperature only impact 
density, and the third case takes into account both effects. The geometry for 
these three cases is unchanged because the fuel is a liquid. However, when 
the graphite blocks heat up, both the density and the geometry change due 
to the thermal expansion of solid graphite. The graphite linear thermal 
expansion is not a dominating factor \cite{li_optimization_2018}, and herein 
we focus only on the Doppler Effect for the moderator temperature coefficient.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [b!]
	\caption{Temperature coefficients of reactivity for 3 different initial 
		fuel salt compositions at startup and equilibrium. Confidence interval 
		$\pm\sigma$ for all coefficients is between $0.11$ and $0.16$ pcm/K).}
	\begin{tabularx}{\textwidth}{ p{0.27\textwidth} | X X  X X  X X } \hline
		\multirow{3}{*}{\shortstack{Reactivity coefficient \\ (pcm/K)}} 
		& 
		\multicolumn{6}{c}{Startup fissile material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil. & Initial & Equil. & Initial & 
		Equil. \\ \hline
		Fuel salt temperature&$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
		\\ 
		Fuel salt density&$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
		Total salt fuel&$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
		\hline
		Graphite temperature&$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
		\\	\hline
		Total core&$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
	\end{tabularx}
	\label{tab:tcoe}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Table~\ref{tab:tcoe} summarizes temperature coefficients calculated for three 
different initial fissile loads at startup and at equilibrium. By propagating 
the $k_{eff}$ statistical error provided by SERPENT-2, uncertainty for each 
temperature coefficient is calculated using the following formula:
\begin{align}
\delta\alpha &= \abs{\frac{1}{T_{i+1} - T_i}} \sqrt{\frac{\delta 
		k_{eff}^2(T_{i+1})}{k_{eff}^4(T_{i+1})}  
	+ \frac{\delta k_{eff}^2(T_i)}{k_{eff}^4(T_i)}}
\intertext{where}
\delta k_{eff} &= \mbox{statistical error for $k_{eff}$ from SERPENT-2 
output.} 
\nonumber
\end{align}

Other sources of uncertainty are neglected, such as cross section measurement 
error and approximations inherent in the density dependence on temperature.

When the fuel salt temperature increases, the density of the salt decreases, 
but at the same time, the total volume of fuel salt in the 
core remains constant because it
is bounded by the vessel. When the graphite 
temperature increases, the density of
graphite decreases, creating additional 
space for the salt. The cross section temperatures for the fuel and moderator 
were changed from 900 to 1000 K to determine the temperature coefficients. 
This work considered five different cases:
\begin{enumerate}
	\item Fuel salt temperature (Doppler Effect) rising from 900 to 1000 K 	
	(first row in Table~\ref{tab:tcoe}).
	\item Fuel salt density decreasing from 3.3 to 3.233 g/cm$^3$ 
	(density change caused by temperature increase from	900 to 1000 K).
	\item Total fuel salt temperature (Doppler+density) rising from 900 to 
	1000 K.	
	\item Graphite temperature (Doppler Effect) rising from 900 to 1000 K.
	\item Whole reactor temperature rising from 900 K to 1000 K.
\end{enumerate}

In the first case, the fuel temperature change only impacts cross section 
temperature. In the second case, changes in the fuel temperature only impact 
density, and the third case takes into account both effects. The geometry for 
these three cases is unchanged because the fuel is a liquid. However, when 
the graphite blocks heat up, both the density and the geometry change due 
to the thermal expansion of solid graphite. The graphite linear thermal 
expansion is not a dominating factor \cite{li_optimization_2018}, and herein 
we focus only on the Doppler Effect for the moderator temperature coefficient.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [b!]
	\caption{Temperature coefficients of reactivity for 3 different initial 
		fuel salt compositions at startup and equilibrium. Confidence interval 
		$\pm\sigma$ for all coefficients is between $0.11$ and $0.16$ pcm/K).}
	\begin{tabularx}{\textwidth}{ p{0.27\textwidth} | X X  X X  X X } \hline
		\multirow{3}{*}{\shortstack{Reactivity coefficient \\ (pcm/K)}} 
		& 
		\multicolumn{6}{c}{Startup fissile material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil. & Initial & Equil. & Initial & 
		Equil. \\ \hline
		Fuel salt temperature&$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
		\\ 
		Fuel salt density&$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
		Total salt fuel&$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
		\hline
		Graphite temperature&$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
		\\	\hline
		Total core&$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
	\end{tabularx}
	\label{tab:tcoe}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
